Comparison to other studies

### 2024-11-07 pages/other_studies.qmd
docs(other studies): adding lots more examples of studies that assessed reproducibility

**In-progress**

TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting --> *struggled to find anything, so maybe just something to mention in general in discussion*

TODO: Add page comparing our findings to other studies. This could include:

* Studies that have gone through this same process of finding barriers in reproductions
* Studies that recommend how to share code (although, it might be simpler to just start with that first bullet and then decide whether to do both)

*Do we also compare the evaluation results? Or do we just use that in context of barriers?* (e.g. @schwander_replication_2021 and @zhang_reporting_2020 for reporting... @laurinavichyute_share_2022 for code...)

@@

Summary of studies that have assessed reproducibility:

| Study | Focus | N | 
| - | - | - |
| @krafczyk_learning_2021 | Articles from *Journal of Computational Physics* | 7 |
| @wood_push_2018 | Impact evaluations in low- and middle-income countries | 109 |
| @schwander_replication_2021 | Health economic obesity models | 4 |
| @laurinavichyute_share_2022 | Articles in the *Journal of Memory and Language* | 59 |
| @konkol_computational_2019 | Geoscientific articles | 31 |
| @hardwicke_analytic_2021 | Articles in *Psychological Science* | 25 |
| @henderson_reproducibility_2024 | Infectious disease models | 200 |
| @samuel_computational_2024 | Jupyter notebooks associated with publications | 3467 publications, from which 27,271 jupyter notebooks were downloaded for further analysis |

The amount they reproduce and so on isn't directly comparable as alot of variation in methods (e.g. amount of troubleshooting allowed, how decided something is reproduced or not, and so on). *not sure if want to be comparing the actual proportions reproduced... or maybe do, but important to bare in mind what is being compared and what define as success... e.g. some include studies that haven't shared the code*

@@

* @laurinavichyute_share_2022
* @konkol_computational_2019
* @hardwicke_analytic_2021

@@

@@

>>>>

@@

### Summary of studies

| Study | Focus | Articles that tried running code from | Brief summary |
| - | - | - | - |
| @chang_is_2022 | Macroeconomics articles | 59 | Of 67 articles, 6 use confidential data and 2 use software they don't have, leaving 59. Of those, replicate 22 without author assistance and 29 with. (Note: no access to article - based on abstract). |
| @eubank_lessons_2016 | Articles in the Quarterly Journal of Political Science which underwent in-house replication review | 24 | Of the 24, 4 didn't require modifications, 13 had code that would run without error, 8 were missing code for results in paper, 7 had no installation directions for dependencies, 14 (58%) had results in paper that differed from code-generated |
| @galiani_incentives_2017 | Economics articles | Unclear | Of 203 included articles, 76% published any data or code. For those that had data and code, 54% of data manipulation code and 61% of "estimation code" could run without major modifications. They found 14% articles fully replicable (raw data to results) and 37% partially (estimated data to results) |
| @konkol_computational_2019 | Geoscientific articles | 41 | Of 41 (R), 2 ran without issue, 33 had resolvable issues, 2 were partially executable, and 4 could not resolve issues. Author assistance for several (e.g. pointing out solutions, sending additional code and data). |
| @krafczyk_learning_2021 | Articles from Journal of Computational Physics | 7 | Attempt to reproduce 7, allow troubleshooting up to 40 hours, success only described via viewing in a figure |
| @henderson_reproducibility_2024 | Infectious disease models | 67 | 200 (100 random, 100 most highly cited). Not reproducible if properietary software/data inaccessible. For random, 19 had code and data. Of those, 4 completedly reproduced and 8 partially. For highly cited, 48 had code and data. Of those, 11 completely reproduced and 22 partially. |
| @mccullough_lessons_2006 | Articles from Journal of Money, Credit and Banking | 58 | Of 266 articles, 193 should have archive entries, but only 69 did. Of those 69, should have code and data, but found only data for 11 of them (i.e. no code). Attempted to use supplied data and code of remaining 58 to reproduce published results. Allowed minor troubleshooting. |
| @obels_analysis_2020 | Registered Reports in psychology | 36 | Of 62 articles, 36 had data and code. Could run 31 and reproduced main results for 21. |
| @samuel_computational_2024 | Jupyter notebooks associated with publications | 15,817 | 3467 publications, from which 27,271 jupyter notebooks were downloaded for further analysis. Of those, 22,578 were Python and 15,817 had dependencies declared in standard file. Attempted to re-run those automatically. 10,388 installed dependencies successfully. Of those, 1203 ran without error - and then 879 had results identical to original, 324 differed |
| @stagge_assessing_2019 | Hydrology and water resources articles | 20 | Looked at data, model and code availability in 360 articles. Of those, 20 had required data/code/directions available for reproduction. Fully reproduce 4, partially reproduced 2, couldn't reproduce 2, and found 10 actually didn't have all the required artefacts. Allowed minor troubleshooting (e.g. folder/file locations) |
| @stockemer_data_2018 | Political science articles | 71 | Looked for data/code in 145 articles, then emailed authors to ask for it. Received data and code for 71. For those, ran code, and success in reproducing apx. 70%. |
| @stodden_enabling_2018 | Articles from Journal of Computational Physics | 55 | Precursor to @krafczyk_learning_2021. Of 306 articles, 55 had code. Spent max 4 hours on them, managed to reproduce some struff for 18, but didn't complete any. |
| @wood_push_2018 | Impact evaluations in low- and middle-income countries | 50 | Of 109, 27 ran to produced comparable results. 59 refused to provide replications files. Of remaining 23, 3 had propreitrary data, 15 had incomplete replication files, and 5 had minor differences in results. | 
: {tbl-colwidths="[20, 25, 15, 40]"}

Examples that use code and/or description in article (i.e. dont' *require* code):

* @laurinavichyute_share_2022 - Articles in the Journal of Memory and Language - Look at data sharing in 59 articles before and 59 articles after a policy is in place. For the 59 after policy, attempted to reproduced. 8 had inaccessible data. Under strict criteria, reproduced 20 (34%). Under lenient criteria, 33 (56%).
* @hardwicke_data_2018 - 35 articles, two team members attempted for each article, used available data and information in article or any other additional documentation
* @hardwicke_analytic_2021 - Articles in Psychological Science - 25 evaluated - initially 16 had at least one "major numerical discprenancy", after troubleshooting with/without authors, 37 discrepancnies remained from 789 checked values
* @ostermann_advancing_2017 - reproducibility required full data set + executable tools or precise step-by-step instructions

Examples that reuses data and repeats analysis "exactly as described in report" with clarification if needed:

* @schwander_replication_2021 - 4 health economic obesity models
* @naudet_data_2018
* @raff_step_2019
* @artner_reproducibility_2021
* @maassen_reproducibility_2020

### Which studies are most relevant? How do they compare?

Note: It is difficult to make comparisons between all these studies due to the large variation in methods (such as amount of troubleshooting allowed, or thresholds for deciding something is reproduced). As such, the actual percentage reproduced is difficult to compare.

However, this section does try to pull out the more relevant studies (in terms of their focus and/or methods), and consider the **similarities and differences** to our work (e.g. broadly considering reproduction findings, but focusing particularly on **issues encountered** and **recommendations made**).

<!--TODO: Write this section -->

**Similar focus**: @henderson_reproducibility_2024

* Infectious disease models (i.e. models, health)

::: {.callout-note collapse="true"}

## Some old rough notes

@@

    * "We **investigated whether the CHEERS score might be predictive for the success of model replication**, but this was not the case, with scores ranging from 18 to 20. The non-successful replication case study 1 rated a score of 19 (the maximum possible CHEERS score is 24). A **comparable finding was observed by another research team that investigated the Phillips checklist** [24] in the context of model replication; they found that the Phillips checklist was not reliable for ensuring that studies are replicable [2]." They then **propose changes** to CHEERS that might help with replicability

@@

:::

## Studies that evaluated research artefacts and/or articles

<!--TODO: Look into this -->

e.g. @schwander_replication_2021 and @zhang_reporting_2020 for reporting... @laurinavichyute_share_2022 for code...

@@

* @gil_toward_2016
    * Proposed checklits for things to include in paper, grouped into categories of:
        * Data accessibility
        * Data documentation
        * Software accessibility
        * Software documentation
        * Provenance documentation
        * Methods documentation
        * Authors identification
    * Suggest papers enriched with metadata/artefacts

## Journal procedures

<!--TODO: Finish this -->

*Psychological Science*

*Quarterly Journal of Political Science* in-house replication review - @eubank_lessons_2016

*Cortex* Verification Reports - @chambers_verification_2020

@galiani_incentives_2017 surveys journals about policies on sharing data and code

Journal of Memory and Language  - open data and code policy, requiring code and data to be released

Vadose Zone Journal - "Reproducible Research" programme where code and data is published alongside article - @skaggs_reproducible_2015
